Patchwork: Incremental Computation for Static Analysis

### 2018-10-14 paper.tex
add a version of the analysis loop with explicit names

\usepackage{listings}

@@

@@

let visitloc : Inv -> Loc -> VisitRes =
  lam inv loc. 
    ...(elided program analysis logic)...
    ...
    ...   let inv' = update inv name loc absstate ;
    ...   Change inv'
    ...
    ...(elided program analysis logic)...

letrec loop : Inv -> Q -> Inv =
  lam inv q.
    match pop q with
      None -> inv
      Some q loc ->
         match visitloc loc inv with
           NoChange -> loop inv q
           Change inv -> loop inv (push q (succof loc))    
\end{lstlisting}
\end{figure}

>>>>

\usepackage{listings}
\lstset{}

@@

% Darker versions (dRed, dBlue, etc.) of common colours;
% pure red/blue/green are violently garish, and too light in monochrome.
%
% dDkRed, etc. are darker still.
% dLight[er]{Blue|Purple} are lighter colours suitable for backgrounds.
%
% dFaint, dGray, dDark, dAlmostBlack are shades of gray.
%
\definecolor{dRed}{rgb}{0.65, 0.0, 0.0}
\definecolor{dDkRed}{rgb}{0.35, 0.0, 0.0}
\definecolor{dGreen}{rgb}{0.0, 0.65, 0.0}
\definecolor{dDkGreen}{rgb}{0.0, 0.35, 0.0}
\definecolor{dBlue}{rgb}{0.0, 0.0, 0.65}
\definecolor{dLightBlue}{rgb}{0.4, 0.4, 0.9}
\definecolor{dLighterBlue}{rgb}{0.8, 0.8, 1.0}
\definecolor{dDkBlue}{rgb}{0.0, 0.0, 0.45}
\definecolor{dLightPurple}{rgb}{0.9, 0.5, 0.9}
\definecolor{dLighterPurple}{rgb}{1.0, 0.7, 1.0}
\definecolor{dPurple}{rgb}{0.65, 0.0, 0.65}
\definecolor{dDigPurple}{rgb}{0.5, 0.0, 0.5}
% \definecolor{DDIGPURPLE}{rgb}{0.5, 0.0, 0.5}  % laughable
\definecolor{dFaint}{rgb}{0.7, 0.7, 0.7}
\definecolor{dGray}{rgb}{0.5, 0.5, 0.5}
\definecolor{dDark}{rgb}{0.2, 0.2, 0.2}
\definecolor{dAlmostBlack}{rgb}{0.1, 0.1, 0.1}

%%% ------- Fungi code in latex listings:
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkpurple}{rgb}{0.5,0,0.5}
\lstset{emph={Nm, Nat, Ref, Type, type, match, with, if, then, else, not, in, let, letrec, ref, get, thunk, force, scope, leaf, NmSet, Nat, Nm, idxtm, nmtm},
  %emphstyle={\color{blue}\bfseries},
  emphstyle={\bfseries},
  keywordstyle={\bfseries},
  commentstyle={\color{darkpurple}\ttfamily},
  language=C,
  showstringspaces=false,
}%
\lstset{emph={[2]%  
    true, false,
    },emphstyle={[2]\color{darkgreen}\bfseries}%,
}%
\newcommand{\code}[1]{\lstinline[basicstyle=\ttfamily]|#1|}
\newcommand{\hlcode}[1]{{\hl{\texttt{#1}}}}
\newcommand{\vttfamily}{\fontfamily{cmvtt}\selectfont}
\lstset{
%basicstyle=\fontsize{7}{8}\ttfamily,
basicstyle=\fontsize{8}{9}\ttfamily,
mathescape=true,
literate={lam~}{$\lambda$}1
         %%%%%%%%%%% Arrows
         %%%%%%%%%%% ---------------------
         {...}{${\color{blue}{\cdots}}$}3
         {=>}{$\Rightarrow$}2
         {<=}{$\leq$}2
         {->}{$\rightarrow$}2
         {nm->}{$\rightarrow$}2 %-- Name term function sort
         {idx->}{$\rightarrow$}2 %-- Index term function sort
         {idx=>}{$\Rightarrow$}2 %-- Kind arrow: sort to kind
         %% {->}{${\color{dBlue}{\rightarrow}}$}2
         %% {nm->}{${\color{dPurple}{\rightarrow}}$}2 %-- Name term function sort
         %% {idx->}{${\color{dRed}{\rightarrow}}$}2 %-- Index term function sort
         %% {idx=>}{${\color{dRed}{\Rightarrow}}$}2 %-- Kind arrow: sort to kind
         %%%%%%%%%% Balanced delims:
         %%%%%%%%%% --------------------------------
         % {{ ... }} = Name set literals (index terms)
         {<~}{${\color{dRed}{\left\{\right.}}$}1
         {~>}{${\color{dRed}{\left.\right\}}}$}1
         % [[ ... ]] = Annotations of types with index terms (e.g., name sets)
         {[[}{${\color{dRed}{\left[\right.}}$}1
         {]]}{${\color{dRed}{\left.\right]}}$}1
         % <[ ... ]> = Annotations of names (e.g., Write scope)
         {<[}{${\color{dRed}{\left<\right.}}$}1
         {]>}{${\color{dRed}{\left.\right>}}$}1
         % [< ... >] = Thunk boundaries in concrete expression syntax
         {[<}{${\color{blue}{\left\{\right.}}$}1
         {>]}{${\color{blue}{\left.\right\}}}$}1
         % << ... ,, ... >> = Binary name composition; primitive form
         {<<}{${\color{dPurple}{\left<\right.\hspace{-4pt}\left<\right.}}$}1
         {>>}{${\color{dPurple}{\left.\right>\hspace{-4pt}\left.\right>}}$}1
         {,,}{${\color{dPurple}{,}}$}1
         %%%%%%%%%%
         %%%%%%%%%% Operators, and index term syntax:
         %%%%%%%%%% ---------------------------------
         {~@~}{${\color{dPurple}{\bullet}}$}1 %-- Binary name composition (for Nm sort)
         {~@@~}{${\color{dRed}{\bullet}}$}1 %-- Binary name composition (for NmSet sort)
         {~*}{${}^{{\color{dRed}{\ast}}}$}1 %-- Kleene star; for an index term function over an initial set
         {@}{{\textcolor{violet}{@}}}1 %-- Name literal/constant
         {^}{${\color{dRed}{\bot}}$}1 %--- Apart symbol
         {forall~}{${\color{dRed}{\forall}}$}1 %--- Forall index terms
         {exists~}{${\color{dRed}{\exists}}$}1 %--- Exists index term
         {writeset~}{${\color{dRed}{\rhd}}$}1  %--- Write set (part of a computation type)
         %%%%%%%%% Sorts:
         %{NmSet}{{\color{dRed}{NmSet}\color{black}}}4
         %% {leaf}{{\color{dPurple}{leaf}\color{black}}}3
         %% {Nm~}{{\color{dPurple}{Nm}\color{black}}}2
         %% %{Nat~}{{\color{dRed}{Nat}\color{black}}}4
         {Nat~}{Nat}4
         %% %%%%%%%%%% Declarations
         %% %%%%%%%%%% ------------------------------------
         %% {idxtm}{{\color{dRed}{idxtm}\color{black}}}4
         %% {nmtm}{{\color{dPurple}{nmtm}\color{black}}}4
}

@@

let visitloc : Inv -> Loc -> VisitRes =
  lam~inv.lam~loc.
    ...
    ...   // subcase: Update the invariant mapping:
    ...   let inv' = update inv loc absstate ;
    ...   Change inv'
    ...

letrec loop : Inv -> Q -> Inv =
  lam~inv.lam~q.
    match pop q with
      None => inv
      Some q loc =>
         match visitloc loc inv with
           NoChange   => loop inv q
           Change inv => loop inv (push q (succof loc))    
\end{lstlisting}
\caption{Analysis loop: Each ``visit'' to a program location has the
  potential to \code{update} the invariant mapping \code{inv}; the
  queue~{q} controls the schedule of these visits. }
\end{figure}

\begin{figure}
\begin{lstlisting}
/// Version with explicit naming strategy
type Q[X:NmSet]
type Inv[X:NmSet]
type VisitRes[X:NmSet] = NoChange | Change (Inv[X])

let visitloc : Inv[X] -> Loc[Y] -> exists Z|Z^X. VisitRes[X^Z] =
  lam~inv.lam~loc.
    ...
    ...   // Construct a name Z such that Z^X
    ...   let name : Nm[Z] = ... ;
    ...   let inv' = update inv name loc absstate ;
    ...   Change inv'
    ...

letrec loop : Inv[X] -> Q[Y] -> exists Z|Z^X. Inv[X^Z] =
  lam~inv.lam~q.
    match pop q with
      None => inv
      Some q loc =>
         match visitloc loc inv with
           NoChange   => loop inv q
           Change inv => loop inv (push q (succof loc))
\end{lstlisting}
\caption{Analysis loop: Each ``visit'' to a program location has the
  potential to \code{update} the invariant mapping \code{inv}; the
  queue~{q} controls the schedule of these visits. }
\end{figure}
